KidsAIR: exposure model

### 2020-03-24 exposure_initial_analysis.Rmd
merge datasets

---
title: "KidsAIR: initial exposure analysis"
author: "Ethan Walker"
date: "Started 2 Feb 2020, Updated 17 March 2020"
output: pdf_document
---

@@

# Mean PM for each placebo home over winter 1
pm_home_mean <- pm_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  #filter(pm < 500) %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  group_by(area, home) %>% 
  summarize(mean_pm = mean(pm, na.rm = TRUE))
```

# Demographics
```{r}
pm_demographics <- pm_home_mean %>% 
  left_join(demographics_clean, by = c("area", "home")) %>% 
  filter(winter_id == 1) %>% 
  mutate(income = fct_collapse(income,
                               "Less than $20,000" = "Less than $20,000",
                               "$20,000-$49,999" = 
                                 c("$20,000 to $29,999", "$30,000 to $39,999",
                                   "$40,000 to $49,999"),
                                "$50,000+" = 
                                 c("$50,000 to $74,999", "$75,000 to $99,999",
                                   "$100,000 or more")),
         income = factor(income, levels = c("Less than $20,000", 
                                            "$20,000-$49,999", 
                                            "$50,000+"))) %>% 
  mutate(education = fct_collapse(education,
                                  "High school or less" = 
                                    c("Less than high school", 
                                      "High school diploma or GED"),
                                  "Some college" = "Some college",
                                  "College degree" = "College degree"),
         education = factor(education, levels = c("High school or less", 
                                            "Some college", 
                                            "College degree"))) %>% 
  mutate(race_parent = fct_collapse(race_parent,
                                    "White" = "White",
                                    "Non-white" = 
                                      c("American Indian/Alaskan Native",
                                        "Asian", "More than one race")),
         race_parent = factor(race_parent, levels = c("White", "Non-white"))) %>% 
  mutate(race_child = fct_collapse(race_child,
                                    "White" = "White",
                                    "Non-white" = 
                                      c("American Indian/Alaskan Native",
                                        "More than one race")),
         race_child = factor(race_child, levels = c("White", "Non-white"))) %>%
  mutate(total_residents = fct_collapse(total_residents,
                                    "<5" = c("1", "2", "3", "4"),
                                    "5+" = c("5", "6", "7", "8", "9", "10",
                                             "11", "12", "13", "14", "15")),
         total_residents = factor(total_residents, levels = c("<5", "5+"))) %>%
  mutate(residents_under_five = fct_collapse(residents_under_five,
                                    "1" = c("0", "1"),
                                    "2+" = c("2", "3", "4", "5")),
         residents_under_five = factor(residents_under_five, levels = c("1", "2+"))) %>% 
  distinct(mean_pm, .keep_all = TRUE)

table(pm_demographics$income)

pm_demographics_results <- lm(mean_pm ~ residents_under_five, data = pm_demographics)
summary(pm_demographics_results)
plot(pm_demographics_results)
```

# Home characteristics
```{r}
pm_home_char <- pm_home_mean %>% 
  left_join(home_char_clean, by = c("area", "home")) %>% 
  filter(winter_id == 1) %>% 
  mutate(home_type = fct_collapse(home_type,
                                  "House" = "House",
                                  "Other" = c("Duplex/Apt", "Mobile Home", "Other")),
         home_type = factor(home_type,
                            levels = c("House", "Other")),
         home_year_built_cat = cut(home_year_built, breaks = c(0, 1985, 2020),
                                 labels = c("<1985", "1985+"),
                                 right = FALSE),
         stove_age = factor(stove_age,
                         levels = c("0-5 years old", "6-10 years old",
                                    "11-15 years old", "16 + years old",
                                    "Do not know")),
         stove_age = fct_collapse(stove_age,
                                  "0-5 years old" = "0-5 years old",
                                  "6-15 years old" = c("6-10 years old",
                                                       "11-15 years old"),
                                  "16 + years old" = "16 + years old",
                                  "Do not know" = "Do not know"),
         stove_cert = factor(stove_cert,
                             levels = c("Yes", "No", "Do not know")),
         home_sqft_cat = cut(home_sqft, breaks = c(0, 1400, 5000),
                         labels = c("<1400", "1400+"),
                         right = FALSE),
         home_floors_cat = cut(home_floors, breaks = c(0, 2, 4),
                                 labels = c("1", "2+"),
                                 right = FALSE),
         home_bedrooms_cat = cut(home_bedrooms, breaks = c(0, 3, 10),
                                 labels = c("<3", "3+"),
                                 right = FALSE),
         home_windows_cat = cut(home_windows, breaks = c(0, 10, 50),
                                labels = c("<10", "10+"),
                                 right = FALSE),
         home_pets_cat = cut(home_pets, breaks = c(0, 2, 50),
                                labels = c("<2", "2+"),
                                 right = FALSE),
         home_furry_cat = cut(home_furry, breaks = c(0, 2, 50),
                                labels = c("<2", "2+"),
                                 right = FALSE),
         secondary_heat = fct_collapse(secondary_heat,
                                       "Electric" = "Electrical",
                                       "Wood stove" = "Wood stove",
                                       "Other" = c("Natural gas furnace",
                                                   "Oil", "Other", "Propane")),
         chimney_clean = factor(chimney_clean,
                         levels = c("Less than 6 months ago", "6-12 months ago",
                                    "12-18 months ago", "More than 18 months ago")),
         chimney_clean = fct_collapse(chimney_clean,
                                  "Less than 6 months ago" = "Less than 6 months ago",
                                  "6-12 months ago" = "6-12 months ago",
                                  "12 + months ago" = c("12-18 months ago",
                                                        "More than 18 months ago")),
         home_damp = factor(home_damp, levels = c("Yes", "No", "Do not know")),
         home_mold = factor(home_mold, levels = c("Yes", "No", "Do not know")),
         home_fireplace = factor(home_fireplace, levels = c("Yes", "No", "Do not know")),
         home_furnace = factor(home_furnace, levels = c("Yes", "No", "Do not know")),
         home_insert = factor(home_insert, levels = c("Yes", "No", "Do not know")))

table(pm_home_char$home_insert)
median(pm_home_char$home_furry, na.rm = TRUE)

pm_home_char_results <- lm(log(mean_pm) ~ home_insert, data = pm_home_char)
summary(pm_home_char_results)
plot(pm_home_char_results)
```

# Stove use
```{r}
pm_stove_use <- pm_home_mean %>% 
  left_join(stove_use_clean, by = c("area", "home")) %>% 
  filter(winter_id == 1) %>% 
  mutate(burn_level = fct_collapse(burn_level,
                                   "No/Light burning" = c("No burning", 
                                                          "Light burning"),
                                   "Ave burning" = "Average burning",
                                   "Heavy burning" = "Heavy burning"),
         burn_level = factor(burn_level,
                         levels = c("No/Light burning", "Ave burning", "Heavy burning")),
         wood_collect = fct_collapse(wood_collect,
                                   "<3 months" = c("< 1 week", "1 week to 1 mo",
                                                   "1 mo to 3 mo"),
                                   "3+ months" = c("3 mo to 6 mo", 
                                                   "6 mo to 1 year", "> 1 yr")),
         wood_collect = factor(wood_collect,
                         levels = c("<3 months", "3+ months")),
         wood_collect_method = fct_collapse(wood_collect_method,
                                   "Harvest yourself" = "Harvest yourself",
                                   "Purchase/other" = c("Mix", "Other", 
                                                        "Purchase it")),
         wood_cords = if_else(wood_cords > 10, 10, wood_cords),
         wood_cords_cat = cut(wood_cords, breaks = c(0, 5, 50),
                                labels = c("<5", "5+"),
                                 right = FALSE))

table(pm_stove_use$wood_cords_cat)
median(pm_stove_use$wood_cords, na.rm = TRUE)

pm_stove_use_results <- lm(log(mean_pm) ~ wood_collect_method, data = pm_stove_use)
summary(pm_stove_use_results)
plot(pm_stove_use_results)
pm_stove_use_plot <- pm_stove_use %>% 
  ggplot() + 
    geom_boxplot(aes(burn_level, mean_pm))
pm_stove_use_plot
```

# Stove grades
```{r}
stove_grades <- stove_grades_clean %>% 
  arrange(area, home, winter_id) %>% 
  group_by(home) %>% 
  mutate(stove_grade = if_else(is.na(stove_grade), lead(stove_grade), stove_grade))

pm_stove_grades <- pm_home_mean %>% 
  left_join(stove_grades, by = c("area", "home")) %>% 
  filter(winter_id == 1) %>% 
  mutate(stove_grade = fct_collapse(stove_grade,
                                    "A" = "A",
                                    "C" = "C",
                                    "D or F" = c("D", "F")))

table(pm_stove_grades$stove_grade)

pm_stove_grades_results <- lm(log(mean_pm) ~ stove_grade, data = pm_stove_grades)
summary(pm_stove_grades_results)
anova(pm_stove_grades_results)
plot(pm_stove_grades_results)
pm_stove_grades_plot <- pm_stove_grades %>% 
  ggplot() + 
    geom_boxplot(aes(stove_grade, mean_pm))
pm_stove_grades_plot
```

# Home activity
```{r}
# Join home activity with mean PM and format for analysis
pm_home_act <- pm_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  arrange(area, home, sampling_day) %>% 
  group_by(area, home, sampling_day) %>% 
  summarize(mean_pm = mean(pm, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(home_act_day = as.factor(sampling_day)) %>% 
  arrange(area, home, home_act_day) %>% 
  left_join(home_act_clean, by = c("area", "home", "home_act_day")) %>% 
  filter(winter_id == 1)

table(pm_home_act$home_act_sweep)

pm_home_act_results <- lmer(log(mean_pm) ~ home_act_sweep + (1 | home), data = pm_home_act)
summary(pm_home_act_results)
plot(pm_home_act_results, 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(pm_home_act_results), main = "QQ Plot")
```

# Wood moisture content
```{r}
# Join moisture content with mean PM and format for analyzis
pm_homes_placebo <- pm_clean %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime_new, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, pm_home, first_datetime_new) %>% 
  separate(first_datetime_new, c("first_date", "first_time"), sep = " ", remove = TRUE) %>% 
  ungroup() %>% 
  arrange(area, home)

moisture_filtered <- moisture_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_placebo, by = c("area", "home", "home_winter_id")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  ungroup() %>%
  arrange(area, home)

moisture_filtered_time <- moisture_filtered %>% 
  # fix wrong date
  mutate(moisture_date = as.character(moisture_date),
         moisture_date = if_else(home == "CH220" & moisture_date == "2014-04-10",
                                 "2017-04-10", moisture_date),
         moisture_date = ymd(moisture_date)) %>% 
  mutate(moisture_date = ymd(moisture_date),
         first_date = ymd(first_date),
         time_diff = moisture_date - first_date,
         time_diff = as.numeric(abs(time_diff))) %>% 
  group_by(home) %>% 
  mutate(time_diff_rank = if_else(time_diff == min(time_diff, na.rm = TRUE), 1, 0)) %>%
  ungroup() %>% 
  filter(time_diff_rank == 1)

pm_moisture <- pm_home_mean %>% 
  left_join(moisture_filtered_time, by = c("area", "home")) %>% 
  filter(winter_id == 1) %>% 
  mutate(moisture_ave_5 = moisture_ave/5,
         moisture_cat = cut(moisture_ave, breaks = c(0, 10, 50),
                                labels = c("<10", "10+"),
                                 right = FALSE))

table(pm_moisture$moisture_cat)
median(pm_moisture$moisture_ave, na.rm = TRUE)

pm_moisture_results <- lm(log(mean_pm) ~ moisture_cat, data = pm_moisture)
summary(pm_moisture_results)
plot(pm_moisture_results)
```

@@

pm_home_act_results <- lm(log(mean_pm) ~ rh_min_cat, data = pm_temp_rh)
summary(pm_home_act_results)
plot(pm_home_act_results)
```

# SUMs 
```{r}
#### Join PM dataset with full SUMs dataset

pm_join <- read_rds("Output/pm_clean.rds") %>% 
  mutate(sample_datetime = ymd_hms(pm_datetime_new)) %>% 
  separate(sample_datetime, c("sample_date", "sample_time"), sep = " ", remove = FALSE) %>% 
  group_by(area, home) %>% 
  arrange(sample_datetime) %>% 
  mutate(pm_last_datetime = last(sample_datetime),
         pm_first_datetime = first_datetime_new,
         sample_datetime = round_date(sample_datetime, unit = "minute"),
         pm_rolling_20 = rollmean(pm, 20, fill = "extend")) %>% 
  ungroup() %>% 
  arrange(area, home, sample_datetime)

sums_join <- read_rds("Output/sums_clean.rds") %>% 
  mutate(sample_datetime = ymd_hms(datetime_sums)) %>% 
  separate(sample_datetime, c("sample_date", "sample_time"), sep = " ", remove = FALSE) %>% 
  mutate(sample_datetime = round_date(sample_datetime, unit = "minute")) %>% 
  ungroup() %>% 
  arrange(area, home, sample_datetime)

@@

pm_sums_events_joined <- pm_home_mean_date %>% 
  left_join(sums_events_27, by = c("area", "home", "date_sums")) %>% 
  filter(sums_event == 1) %>% 
  arrange(area, home, date_sums) %>% 
  group_by(area, home, mean_pm) %>% 
  summarize(sums_events = n()) %>% 
  #mutate(sums_events = factor(sums_events))
  mutate(sums_events_cat = cut(sums_events, breaks = c(0, 1, 10),
                           labels = c("1", ">1")))

median(pm_sums_events_joined$sums_events)

pm_sums_model <- lmer(mean_pm ~ sums_events_cat + (1 | home), data = pm_sums_events_joined)
pm_sums_model <- lmer(log(mean_pm) ~ sums_events_cat + (1 | home), data = pm_sums_events_joined)

summary(pm_sums_model)
#exp((0.146291)-1)*100
plot(pm_sums_model, 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(pm_sums_model), main = "QQ Plot")
```

>>>>

---
title: "KidsAIR: initial exposure analysis"
author: "Ethan Walker"
date: "Started 2 Feb 2020, Updated 20 March 2020"
output: pdf_document
---

@@

# Mean PM for each placebo home over winter 1
pm_home_mean <- pm_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  #filter(pm < 500) %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  group_by(area, home) %>% 
  summarize(mean_pm = mean(pm, na.rm = TRUE))

exposure_analysis_data_long <- read_rds("Output/exposure_analysis_data_long.rds")

exposure_analysis_data_short <- read_rds("Output/exposure_analysis_data_short.rds") 
```

# Demographics
```{r}
filter_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(pm_mean))

# Variables to use:
## education_3level, income_3level, race_parent_2level, race_child_2level
## total_residents_2level, residents_under5_2level, resident_smokes

table(filter_data$residents_smoke)
median(filter_data$home_furry, na.rm = TRUE)

pm_demographics_results <- lm(log(pm_mean) ~ residents_smoke, data = filter_data)
summary(pm_demographics_results)
plot(pm_demographics_results)
```

# Home characteristics
```{r}
filter_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(pm_mean))

# Variables to use:
## home_type_2level, home_year_built_2level, home_sqft_2level, home_floors_2level
## home_bedrooms_2level, home_windows_2level, home_pets_2level, home_furry_2level
## secondary_heat_3level, stove_age_3level, stove_cert, chimney_clean_3level,
## home_damp, home_mold, home_fireplace, home_furnace, home_insert

table(filter_data$home_insert)
median(filter_data$home_furry, na.rm = TRUE)

pm_home_char_results <- lm(log(pm_mean) ~ home_insert, data = filter_data)
summary(pm_home_char_results)
plot(pm_home_char_results)
```

# Stove use
```{r}
filter_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(pm_mean))

# Variables to use:
## burn_level_3level, wood_collect_2level, wood_collect_method_2level,
## wood_cords

table(filter_data$home_insert)
median(filter_data$wood_cords, na.rm = TRUE)

pm_stove_use_results <- lm(log(pm_mean) ~ wood_collect_method_2level, data = filter_data)
summary(pm_stove_use_results)
plot(pm_stove_use_results)
pm_stove_use_plot <- pm_stove_use %>% 
  ggplot() + 
    geom_boxplot(aes(burn_level, mean_pm))
pm_stove_use_plot
```

# Stove grades
```{r}
filter_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(pm_mean))

# Variables to use:
## stove_grade_3level

table(filter_data$stove_grade_3level)

pm_stove_grades_results <- lm(log(pm_mean) ~ stove_grade_3level, data = filter_data)
summary(pm_stove_grades_results)
anova(pm_stove_grades_results)
plot(pm_stove_grades_results)
pm_stove_grades_plot <- pm_stove_grades %>% 
  ggplot() + 
    geom_boxplot(aes(stove_grade, mean_pm))
pm_stove_grades_plot
```

# Home activity
```{r}
filter_data <- exposure_analysis_data_long %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(home) %>% 
  distinct(sampling_day, .keep_all = TRUE) %>% 
  filter(!is.na(pm_mean_sampling_day))

# Variables to use:
## home_act_gas, home_act_elect, home_act_propane, home_act_oil, home_act_other,
## home_act_smoke, home_act_incense, home_act_candle, home_act_windows,
## home_act_door, home_act_sweep

table(filter_data$home_act_sweep)

pm_home_act_results <- lmer(log(pm_mean_sampling_day) ~ home_act_sweep + 
                              (1 | home), data = filter_data)
summary(pm_home_act_results)
plot(pm_home_act_results, 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(pm_home_act_results), main = "QQ Plot")
```

# Wood moisture content
```{r}
filter_data <- exposure_analysis_data_long %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(!is.na(moisture_ave)) %>% 
  select(sample_date, pm_first_datetime, area, home, 
         moisture_ave, pm_mean_sampling_period) %>% 
  separate(pm_first_datetime, c("pm_first_date", "first_time"), sep = " ") %>% 
  group_by(area, home) %>% 
  mutate(moisture_date = ymd(sample_date),
         first_date = ymd(pm_first_date),
         time_diff = moisture_date - first_date,
         time_diff = as.numeric(abs(time_diff))) %>% 
  group_by(home) %>% 
  mutate(time_diff_rank = if_else(time_diff == min(time_diff, na.rm = TRUE), 1, 0)) %>%
  ungroup() %>% 
  filter(time_diff_rank == 1) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(pm_mean_sampling_period))

# Variables to use:
## moisture_ave, mean_moisture_5

table(filter_data$moisture_cat)
median(filter_data$moisture_ave, na.rm = TRUE)

pm_moisture_results <- lm(log(pm_mean_sampling_period) ~ 
                            moisture_ave, data = filter_data)
summary(pm_moisture_results)
plot(pm_moisture_results)
```

@@

pm_home_act_results <- lm(log(mean_pm) ~ rh_min_cat, data = filter_data)
summary(pm_home_act_results)
plot(pm_home_act_results)
```

# SUMs - experimenting with several methods of looking at associations
```{r}
#### Join PM dataset full SUMs dataset by SUMs sampling times

pm_join <- pm_clean %>% 
  mutate(sample_datetime = ymd_hms(pm_datetime_new)) %>% 
  separate(sample_datetime, c("sample_date", "sample_time"), sep = " ", remove = FALSE) %>% 
  group_by(area, home) %>% 
  arrange(sample_datetime) %>% 
  mutate(pm_last_datetime = last(sample_datetime),
         pm_first_datetime = first_datetime_new,
         sample_datetime = round_date(sample_datetime, unit = "minute"),
         pm_rolling_20 = rollmean(pm, 20, fill = "extend")) %>% 
  ungroup() %>% 
  arrange(area, home, sample_datetime)

sums_join <- sums_clean %>% 
  mutate(sample_datetime = ymd_hms(datetime_sums)) %>% 
  separate(sample_datetime, c("sample_date", "sample_time"), sep = " ", remove = FALSE) %>% 
  mutate(sample_datetime = round_date(sample_datetime, unit = "minute")) %>% 
  ungroup() %>% 
  arrange(area, home, sample_datetime)

@@

sums_temp_change <- sums_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area, home, date_sums) %>% 
  mutate(time_diff = (lead(datetime_sums) - datetime_sums)/60) %>% 
  mutate(lead_temp = if_else(time_diff < 20, lead(temp_c_sums, 4), lead(temp_c_sums)),
         lead_temp = if_else(time_diff > 25, 999, lead_temp)) %>% 
  replace_with_na(replace = list(lead_temp = 999)) %>% 
  mutate(temp_diff = lead_temp - temp_c_sums,
         temp_diff_abs = abs(lead_temp - temp_c_sums),
         # change temp in the following line
         temp_diff_check = if_else(temp_diff >= 8, 1, 0),
         heat_event = if_else(temp_diff_check == 1 & lag(temp_diff_check) == 1, 0,
                              temp_diff_check),
         heat_event = if_else(is.na(temp_diff_check), 1,
                              heat_event)) %>% 
  ungroup() %>% 
  mutate(date_sums = as.character(date_sums)) %>% 
  group_by(area, home, date_sums) %>% 
  summarize(sums_events = sum(heat_event, na.rm = TRUE)) %>% 
  ungroup() %>% 
  arrange(area, home, date_sums)

pm_sums_events_joined <- pm_home_mean_date %>% 
  left_join(sums_temp_change, by = c("area", "home", "date_sums")) %>% 
  arrange(area, home, date_sums) %>% 
  #mutate(sums_events = factor(sums_events))
  mutate(sums_events_cat = cut(sums_events, breaks = c(0, 2, 20),
                           labels = c("<2", "2+"),
                                 right = FALSE))

median(pm_sums_events_joined$sums_events, na.rm = TRUE)
table(pm_sums_events_joined$sums_events_cat)

pm_sums_model <- lmer(mean_pm ~ sums_events_cat + (1 | home), data = filter_data)
pm_sums_model <- lmer(log(mean_pm) ~ sums_events_cat + (1 | home), data = filter_data)

summary(pm_sums_model)
#exp((0.146291)-1)*100
plot(pm_sums_model, 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(pm_sums_model), main = "QQ Plot")

pm_sums_plot <- pm_sums_events_joined %>% 
  filter(!is.na(sums_events)) %>% 
  ggplot() + 
    geom_boxplot(aes(sums_events_cat, log(mean_pm))) +
    theme_minimal()
pm_sums_plot

```

### 2020-03-24 exposure_models.Rmd
merge datasets

```{r}
exposure_analysis_data_long <- read_rds("Output/exposure_analysis_data_long.rds") %>% 
  filter(!is.na(pm_mean_daily))

exposure_analysis_data_short <- read_rds("Output/exposure_analysis_data_short.rds") %>% 
  filter(!is.na(pm_mean))
```

>>>>

```{r}
exposure_analysis_data_long <- read_rds("Output/exposure_analysis_data_long.rds")

exposure_analysis_data_short <- read_rds("Output/exposure_analysis_data_short.rds") 
```
